---
title: "Forecasting COVID-19 epidemic short term hospital needs in France"
author: Clément Massonnaud^1^^,2^\footnote{Both authors contributed equally.}, Jonathan Roux^1^$^\ast$, Pascal Crépey^1^\footnote{corresponding author - pascal.crepey@ehesp.fr}
include-before: ^1^ Univ Rennes, EHESP, REPERES « Recherche en Pharmaco-Epidémiologie et Recours aux Soins » – EA 7449, 15 avenue du Professeur-Léon-Bernard, CS 74312, 35043 Rennes, France. ^2^ Rouen University Hospital, Department of Biostatistics, 76031 Rouen, France.
date: "`r Sys.Date()`"
knit: "bookdown::render_book"
csl: "../doc/biblio/the-lancet.csl"
documentclass: article
#documentclass: krantz
link-citations: yes
colorlinks: yes
always_allow_html: true
site: bookdown::bookdown_site
fontsize: 11pt
geometry: margin=0.8in
rmd_files: ["index.rmd", "01-intro-method.rmd", "02-results.rmd", "03-discussion.rmd", "09-references.rmd"]
output:
  bookdown::pdf_book:
    toc: false
bibliography: ../doc/biblio/references.bib
#output: rticles::plos_article
#csl: plos.csl
---


```{r echo = F}
knitr::opts_chunk$set(echo = F, cache = T, message = F, warnings = F)
```
```{r cache = F, echo=FALSE, message=FALSE}
# Document and load package (no need to build or install)
#devtools::document()
library(HospiCov)
library(ggplot2)
```


# Abstract

Europe is now considered as the epicenter of the SARS-CoV-2 pandemic, France being one of the most impacted country. In France, there is an increasing concern regarding the capacity of the healthcare system to sustain the outbreak, especially regarding intensive care units (ICU); however, data is lacking. The aim of this study was to estimate the dynamics of the epidemic in France, and to assess its impact on healthcare resources for each French metropolitan Region. We developed a deterministic, age-structured, Susceptible-Exposed-Infectious-Removed (SEIR) model based on catchment areas of each COVID-19 referral hospitals and parametrized with available epidemic information. We estimated until April 14, 2020 in three different scenarios ($R_0=1.5$, $R_0=2.25$, $R_0=3$) the daily number of COVID-19 cases, hospitalizations and deaths, the needs in ICU beds per Region and the reaching date of ICU capacity limits. At the national level, the total number of infected cases is expected to range from 22,872 in the best case ($R_0=1.5$) to 161,832 in the worst case ($R_0=3$). Regarding the total number of deaths, it is expected to vary from 1,021 to 11,032, respectively. At the regional level, all ICU capacities may be overrun in the worst scenario. Only seven Regions may lack ICU beds in the mid scenario ($R_0=2.25$) and only one in the best case. In the three scenarios, Corse may be the first Region to see its ICU capacities overrun. The two other Regions, whose capacity will be overrun shortly after are Grand-Est and Bourgogne-Franche-Comté. While preliminary, our analysis shows that, even in the best case scenario, the French healthcare system will very soon be overwhelmed. While drastic social distancing measures may temper our results, a massive reorganization leading to an expansion of French ICU capacities seems to be necessary to manage the coming wave of critically affected COVID-19 patients.



